### 2024-11-26 acronyms/acronyms.tex
bpc
acronyms
new

\newacronym{cis}{CISSE}{Colloquium for Information Systems Security Education}

@@

>>>>

\newacronym{css}{CISSE}{Colloquium for Information Systems Security Education}

@@

\newacronym{nss}{NASA}{National Aeronautics and Space Administration}
\newacronym{trl}{TRL}{Technology Readiness Level}
\newacronym{nis}{NIST}{National Institute of Standards and Technology}
\newacronym{cvr}{CVaR}{Conditional Value at Risk}
